\newcommand{\coursecontent}{
Systems of Linear Equations
	& $\bullet$ Solving systems of linear equations using Gaussian elimination
	& \S 1.1 prob 1-17, T-F
\\
	& \phantom{$\bullet$} and Gauss-Jordan elimination.
	& \S 1.2 prob 1-32, 35, 36, 37-42,T-F
\\ \textbf{(5 weeks)}
	& $\bullet$ Properties of matrices and matrix algebra.
	& \S 1.3 prob 1-17 (odd), 19- 23,27- 30, T-F
\\
	& $\bullet$ Definition of matrix inverse and more matrix algebra.
	& \S 1.4 prob 4-10,14-17,21, 25-42,51-55,T-F
\\
	& $\bullet$ Properties of elementary matrices, finding inverse matrices.
	& \S 1.5 prob 1-32, 35, 37-43, T-F
\\
	& $\bullet$ Theorems on invertibility and solutions of systems.
	& \S 1.6 prob 1-23, T-F
\\
	& $\bullet$ Diagonal, triangular and symmetric matrices.
	& \S 1.7 prob 1-28,32-39, T-F
\\
	&
	& Supp. Ex. 8-15, 17-21
\\ \hline

The Determinant Function
	& $\bullet$ Evaluating determinants by cofactor expansion.
	& \S 2.1 prob 1-39, T-F
\\
	& $\bullet$ Evaluating determinants by row reduction.
	& \S 2.2 prob 1-17 19-36,T-F
\\ \textbf{(2 weeks)}
	& $\bullet$ Investigating properties of the determinant function.
	& \S 2.3 prob 3,5,7-39,T-F
\\
	& $\bullet$ Finding inverses using the adjoint.
	& Supp. Ex. 16, 31, 32,33
\\
	& $\bullet$ Solving systems of linear equations using Cramer’s Rule
	&
\\ \hline

Euclidean vectors spaces
	& $\bullet$ The geometric definition of a vector, component notation for a vector.
	& \S 3.1 prob 1-31(odd), T-F
\\
	& $\bullet$ Norm of a vector, vector arithmetic.
	& \S 3.2 prob 1-27 (odd), T-F
\\ \textbf{(4 weeks)}
	& $\bullet$ The dot product, vector projections, and applications.
	& \S 3.3 prob 1-40 (odd), T-F
\\
	& $\bullet$ Lines and Planes in Space.
	& \S 3.4 prob 1-25 (odd), T-F
\\
	& $\bullet$ The cross product and its properties and applications.
	& \S 3.5 prob 1-35, T-F
\\
	& The Scalar Triple Product and applications.
	&
\\
	& The following additional topics are covered:
	&
\\
	& \hspace{0.1in} -- Calculations of distance: between 2 skew lines.
	&
\\
	& \hspace{0.1in} -- Near point problems: the closest point on a plane to a point,
	&
\\
	& \hspace{0.1in} \phantom{--} the closest point on a line to a point.
	&
\\
	& Additional problems on lines, planes, distances, and near points will be provided.
	&
\\ \hline

Vector Spaces
	& $\bullet$ Vector space axioms, some properties of vectors.
	& \S 4.1 prob. 2-13,16-23, T-F
\\
	& $\bullet$ Subspaces, linear combinations of vectors, spanning.
	& \S 4.2 prob. 1-5, 7-19, T-F
\\ \textbf{(3 weeks)}
	& $\bullet$ Linear Independence.
	& \S 4.3 prob. 1-10, 13,15,16, T-F
\\
	& $\bullet$ Basis and dimension.
	& \S 4.4 prob. 1-13
\\
	&
	& \S 4.5 prob 1-11, 14
\\
}
