\newcommand{\competencies}{This course will allow the student to fully achieve the competency
\textit{``{\textbf{00UQ:} To apply the methods of linear algebra and vector geometry to problem solving.''}}
and contributes to the partial achievement of the competency
\textit{``\textbf{00UU:} To apply what they have learned to one or more subjects in the sciences''}.}

\newcommand{\firstcompetency}{
	Elements of the competency \textbf{00UQ}:
	\begin{compactenum}
		\item To express concrete problems as linear equations.
		\item To solve systems of linear equations using matrices.
		\item To establish connections between geometry and algebra.
		\item To determine the equation of geometric loci (straight lines and planes) and find their intersections.
		\item To calculate angles, lengths, areas and volumes.
		\item To demonstrate propositions.
		\item To make two -- and three -- dimensional drawings of loci. \\
	\end{compactenum}

	Performance criteria (\textbf{00UQ}):
	\begin{compactitem}
		\item Proper use of concepts.
		\item Representation of situations in terms of vectors and matrices.
		\item Correct application of algorithms.
		\item Correct solution of systems of linear equations.
		\item Adequate representation of loci.
		\item Justification of the steps in the solution.
		\item Algebraic operations in conformity with rules.
		\item Accuracy of calculations.
		\item Correct interpretation of results.
		\item Use of appropriate terminology.
	\end{compactitem}
}
\newcommand{\secondcompetency}{
	Elements of the competency \textbf{00UU}:
	\begin{compactenum}
		\item Recognize the contribution of more than one
		scientific discipline to certain situations.
		\item Apply the experimental method.
		\item Solve problems.
		\item Use data-processing technologies.
		\item Reason logically.
		\item Communicate effectively.
		\item Show evidence of independent learning in their choice of documentation or laboratory instruments.
		\item Work as members of a team.
		\item Make connections between science, technology and social progress. \\
	\end{compactenum}

	Performance criteria (\textbf{00UU}):
	\begin{compactitem}
		\item Use of an interdisciplinary approach
		\item Consistency and rigour in problem-solving, and justification of the approach used
		\item Observance of the experimental method and, where applicable, the experimental procedure
		\item Clarity and precision in oral and written communication
		\item Correct use of the appropriate data-processing technology
		\item Appropriate choice of documents or laboratory instruments
		\item Significant contribution to the team
		\item Appropriate connections between science, technology and social progress
	\end{compactitem}
}
